An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-18 indicators/paper/paper.tex
More figure jostling
Copyedits to discussion

There are a number of open questions, and challenges that remain. Several
signals are subject to biases, such as survey sampling and nonresponse biases,
or geographic differences in market share for medical claims data. Claims data
can also be subject to biases during major national holidays and other events
that change health-seeking behavior. Characterizing these biases will be
important for future research and operational systems that use these
signals. Several data sources are also subject to extensive revision and
backfill, which must be studied and modeled to enable effective real-time use of
these sources in forecasting and nowcasting systems. The breadth and unique
features of the COVIDcast API will help facilitate this work, which will be
vital to advancing pandemic modeling and preparedness.

>>>>

There are a number of open questions, and challenges that remain. Several
signals are subject to biases, such as survey sampling and nonresponse biases,
or geographic differences in market share for medical claims data. Claims data
tends also to be subject to biases during major holidays and other events that
change health-seeking behavior. Characterizing these biases will be important
for future research and operational systems that use these signals. Several data
sources are also subject to extensive revision and backfill, which must be
studied and modeled to enable effective real-time use of these sources in
forecasting and nowcasting systems. The breadth and unique features of the
COVIDcast API will help facilitate this and other related work, which will be
vital to advancing pandemic modeling and preparedness.
